Zohmg---a large scale data warehouse for aggregated time-series-based data. [DRAFT]

### 2009-05-05 doc/report/msc-report.tex
doc/report/msc-report.tex: added info about Python modules. removed REST.

Middleware. WSGI. HTTP server.

@@

@@

\section{REST}

REST\footnote{Representational State Transfer}

>>>>

Python Paste is a framework for building WSGI\footnote{Web Server Gateway
Interface, a HTTP extension where a CGI-like environment is passed around.}
applications and middleware.

WSGI applications receive a WSGI request and returns a response with the
built-in web server.

Middleware is software that acts as an intermediary. WSGI middleware
receives a WSGI request and then performs logic upon this request, before
passing the request to a WSGI application.

@@

Python Setuptools is a framework---built on top of the Python module
distutils---for basic package management of Python software. Amongst other
things it creates and installs Python Eggs\footnote{A Zip file which
bundles Python software.}.

@@

A simple, fast, complete and extensible JSON encoder and decoder for
Python. The Python module simplejson is implemented entirely in Python and
has no external dependencies. However a C extension which provides a
serious speed boost is included.
